Predicting Transport in Lyotropic Liquid Crystal Membranes with Molecular Dynamics Simulations -- Outline

### 2017-08-28 Ben_Manuscripts/Paper1/Outline.tex
reverse outlining based on masters bypass paper

\documentclass{article}
\title{Predicting Transport in Lyotropic Liquid Crystal Membranes with Molecular Dynamics Simulations -- Outline}
\author{Benjamin J. Coscia, Michael R. Shirts, Douglas L. Gin, Richard D. Noble}
\begin{document}
\bibliographystyle{ieeetr}
\maketitle
\section{Introduction}

Nanostructured membrane materials have become increasingly popular in desalination and wastewater treatment applications because they offer the ability to control membrane architecture at the atomic scale.
\begin{itemize}
	\item Current state-of-the-art reverse osmosis membranes are dense and unstructured with tortuous and polydisperse pores which lead to inconsistent performance
	\item Tortuosity and polydispersity drive up energy requirements which strain developing regions and contribute strongly to CO2 emissions
	\item With nanostructured materials, solute rejecting pores can be tuned uniformly -- drives down energy requirements
\end{itemize}

Development of nanostructured materials has been limited by the ability to synthesize and scale various fundamentally sound technologies.
\begin{itemize}
	\item Leading technologies and their limitations:
	\begin{itemize}
		\item Graphene sheets -atomically thick which gives excellent permeability but defects during manufacturing severely impact performance
		\item Carbon Nanotubes - MD studies are promising but synthetic techniques unable to achieve necessary alignment and pore monodispersity
		\item Zeolites - Good rejections/selectivities, but low flux and high cost of manufacturing. Generally limited to applications needing thermal/chemical resistance
	\end{itemize}
\end{itemize}

Lyotropic Liquid Crystals (LLCs) share the characteristic ability of nanostructured membrane materials to create highly ordered structures with the benefits of low cost and synthetic techniques which may be feasible for large scale production.
\begin{itemize}
	\item Forms lamellar, bicontinuous cubic and hexagonal phase based on solution composition
	\item My monomer forms HII phase consisting of vertically aligned, monodisperse, straight pores in a hexagonal array
	\item Hydrophilic regions point towards pore centers
	\item Until recently, they could not be aligned - hindered progress
	\item Talk about Yale alignment techniques
	\item LLC HII phase membranes offer potential for high permeability and selectivity which equals low energy consumption
\end{itemize}

A molecular level understanding of solute transport in LLC membranes will accelerate development efforts by providing guidelines for monomer design.
\begin{itemize}
	\item HII phase studies currently limited mostly to one monomer with minor variations
	\item Current optimization efforts performed through trial and error
	\item Macroscopic models are the only source of predictive modeling
	\item An atomistic understanding of the mechanism of solute transport can identify
	performance bottle necks and direct design of future monomers/membranes
	\item The arrangement of sodium ions in the channels is thought to be confined to the pore walls. It is possible they are arranged more randomly
	\begin{itemize}
		\item This could change how one thinks about molecules diffusing through membrane
		\item Could also be a difference between lyotropic and thermotropic phases
	\end{itemize}
	\item Will we observe Donnan exclusion or some variation on it at the pore entrance
	\item What are the relative weights of steric and electrical effects that deterimine selectivity -- is there an optimal balance 
	\item How many monomers are in a layer?
	\item What is the equilibrium water content in lyotropic phase?
	\item We can vary the following to make predictions about new systems:
	\begin{itemize}
		\item Liquid crystal used - or a mixture of different liquid crystals
		\item Minor structural variations (e.g. 7, 8, , 9, 10, 11 ... CH2's in the tails)
		\item Counterion -- Size/valence of counterion
		\item Functional head groups
	\end{itemize}
	\item How does varying these things effect pore separation, pore size, phase stability, and transport and why are these effects observed 
\end{itemize}

A physically accurate molecular model with easily modified structural features will launch a new phase of research into directing design of an optimal LLC membrane.
\begin{itemize}
	\item The paper will illustrate the development of a predictive molecular model
	\item Measurements made to validate model
	\item Observations of transport mechanism
	\item The model is consistent with experiments and ready to extend to other systems
\end{itemize}

\section{System Setup}

HII monomers were parameterized using the Generalized Amber Forcefield with the Antechamber package provided with AmberTools16. All molecular dynamics simulations were run using Gromacs version 5.1.2.

The most suitable monomer structural configuration was decided by applying a simulated annealing process to the parameterized monomer. 
\begin{itemize}
	\item Initially parameterized monomer gives unfavorable structure
	\item Structure cooled from 1000 to 50 K over 10 nanoseconds
	\item Result not global minimum but close enough for structure building
	\item Multiple configurations saved from annealing trajectory to prove independence of starting config
\end{itemize}

The timescale for self assembly of monomers into the hexagonal phase is unknown and likely outside of a reasonable simulation length. 
\begin{itemize}
	\item Work done that shows coarse grain model self assembly in ~1000 ns
	\item Attempts with HII system not fruitful
	\item Wrote own code to assemble monomers into HII configuration (described in intro) close to what is expected -- equilibration simulations allow structure to relax into expected configuration 
	\item Code has adjustable parameters: Pore-to-Pore distance, pore radius, number of monomer layers (justification for parameters chosen in following paragraphs)
	\item This is the thermotropic phase, information used depends on thermotropic experimental data
\end{itemize}

After some experimentation, it was found that twenty monomer layers per pore provided a balance of structural accuracy and computational efficiency. 
\begin{itemize}
	\item Space between membrane layers in z direction - semi-isotropic sims fix z box dimension
	\item Small number of layers create micellar structure
	\item Beyond 20 layers is unnecessary to get expected configuration
\end{itemize}

The starting distance between layers was chosen so that energy minimization occured with no errors due to overlaps. 
\begin{itemize}
	\item Layers collapse to favorable layer-to-layer distance within first few picoseconds of equilibration 
\end{itemize}

\noindent The remaining parameters were chosen based on experimental data. 
\begin{itemize}
	\item SAXS to get Pore-to-Pore
	\item TEM images estimate pore size
\end{itemize}

\noindent NPT simulations were run at 300 K and 1 bar for system equilibration. 
\begin{itemize}
	\item Monitored 'hexagonality'
	\item Pores don't show perfect hexagonal character for short sims (~20 ns) 
	\item We see a smaller average pore-to-pore distance than reported
	\item Varied initial pore-to-pore distance and ran very long simulations
	\item Starting pore-to-pore distances of 4.0 and 4.5 converge to same average with long\textbf{er} sims 
\end{itemize}

After an equilibrated structure was created, a crosslinking procedure was performed in order to better parallel synthetic procedures. 
\begin{itemize}
	\item Crosslinking maintains alignment of cylindrical mesophases
	\item head to tail addition
	\item Details of crosslinking algorithm (refer to appendix or supplemental info)
\end{itemize}

\noindent The crosslinked system was then solvated with water to mimic a membrane in water.
\begin{itemize}
	\item x ns sims run to allow full water penetration into pores
	\item simulated isotropically with enough water in between periodic images
\end{itemize}

\section{Results and Discussion}

The final, equilibrated system had pores which were spaced 3.5 nm apart. This is the thermotropic phase though. More to come once system is solvated.

Other things to be studied:
\begin{itemize}
	\item Monomers per layer
	\begin{itemize}
		\item Questions: How many monomers are in each layer? Do we observe pi stacking of benzene rings as hypothesized in papers? Are there even defined layers?
		\item Hypothesis: There are an average of 7 monomers per layer when defined per unit volume but there are not well-defined layers as pictured in the literature. While long range order is maintained, hexagonal mesophases are disordered within their hydrophilic and hydrophobic domains. Staying completely ordered, stacked on top of each other is not entropically favorable.
	\end{itemize}
	\item Self diffusion of sodium in pores
	\begin{itemize}
		\item Past literature reports ions arranged in a circle about pore walls leaving void space as a pore. Simulation show that they may be arranged gaussian-like	
		\item Ions may play a different role in transport than previously thought. They might hinder transport by slowing diffusion of other sodiums and molecules. 
		\item Questions to be studied: Do sodium counter-ions stay bound to carbonyl groups? Do sodium ions that get through the membrane need to go all the way through or do they cause some sort of momentum transfer that pushes a different ion out of the pore on the opposite side? Is there ion diffusion through hydrophobic matrix? Is it negligible? What happens to the chlorine ion in NaCl?
		\item Hypothesis: Sodium ions that are already acting as counterions stay mostly bound to their functional groups. Sodium ions diffusing through from bulk salt water need to diffuse all the way through and drag along a chlorine atom to maintain charge neutrality. Sodium ions tethered to chloride may exchange with sodium ions bound to monomer. There is negligible diffusion of sodium chloride through hydrophobic matrix.
	\end{itemize}
	\item Diffusion of water in pores
	\begin{itemize}
		\item Questions to be studied: How easily does water diffuse through the pores (permeability)? Is there diffusion at all through the hydrophobic matrix? If so, is it negligible? Is there a hydration shell around entering salt? Do waters get stripped from hydration shell? How does water interact with sodium ions? Is water transport faster down the center of the pore? Do water molecules orient themselves in a specific way at the pore walls?
		\item Hypothesis: Water molecules will travel with through the pores with a parabolic laminar-like trajectory. Water molecules along the wall will be hindered as they get stuck in the hydrophilic head groups causing slower transport at the walls -- This hypothesis will depend on what I see once I solvate and equilibrate the system with water. I think the arrangement of sodium ions will change when solvated (That could be an intersting conclusion in itself). No water will be transported through hydrophobic regions.    
	\end{itemize}
	\item Compare rates of diffusion of water and sodium to estimate selectivity and rejection
	\begin{itemize}
		\item I am studying this because they are the two parameters to be optimized ultimately
	\end{itemize}
\end{itemize}

\section{Conclusion}

In this work, a molecular model has been developed which can predict transport in an lyotropic liquid crystal membrane. 
\begin{itemize}
	\item Results presented for HII phase monomer but can be adapted to other LLCs
	\item Model can be used for prediction of transport properties in new membranes
\end{itemize}

\end{document}

>>>>

\documentclass{article}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage{geometry}
\geometry{legalpaper, margin=1in}
\usepackage{amsmath} % or simply amstext
\newcommand{\angstrom}{\textup{\AA}}
\title{Predicting Transport in Lyotropic Liquid Crystal Membranes with Molecular Dynamics Simulations -- Outline}
\author{Benjamin J. Coscia \and Douglas L. Gin \and Richard D. Noble \and Joe Yelk \and Matthew Glaser \and Xunda Feng \and Michael R. Shirts} 
\begin{document}
  \bibliographystyle{ieeetr}
  \graphicspath{{./figures/}}
  \maketitle
  \section*{Introduction}

  Nanostructured membrane materials have become increasingly popular for 
  aqueous separations applications such as desalination and biorefinement
  because they offer the ability to control membrane architecture at the
  atomic scale allowing the design of solute-specific separation membranes

  While RO and NF have seen many advances in the past few decades, they 
  are far from perfect separation technologies.

  Nanostructured membranes can bypass many of the performance issues which
  plague traditional NF and RO membranes.

  Development of nanostructured materials has been limited by the ability
  to synthesize and scale various fundamentally sound technologies.

  Self assembling lyotropic liquid crystals (LLCs) are a suitable candidate
  for aqueous separation applications.

  A molecular level understanding of LLC membrane structure will elucidate
  small molecule transport mechanisms, providing guidelines to reduce the
  chemical space for the design of monomers used to create separation-specific
  membranes.

  A clear picture of the nanoscopic LLC membrane structure, gained by building 
  a molecular model will provide evidence to answer existing and newly proposed
  questions.

  We must show that the developed molecular model is consistent with
  physical observations so that we can rely on conclusions drawn about % better word for trust?
  structural features characteristic of the system.
